|

### 2025-01-25 doc/paper.qmd
added theoretical background on types of replication; daily stock data methodlolgy;

Building on these foundations, Assignment III investigates the informativeness of quarterly earnings announcements and their contribution to annual share price movements. The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets. By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting. The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively. Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S. country to explore cross-market variations.

@@

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task1 establishes baseline results by replicating key tables and figures from the original study using US data (1972–2006). @sec-task2 extends the analysis by applying the same methodology to 2007–2023 US data, enabling a comparison of how results evolve over time. @sec-task3 broadens the scope by applying the approach to a non-US country, requiring adjustments for different databases and market structures. Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper. The concluding remarks are provided in @sec-conclusion.

@@

Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using US data (1972–2006) to establish baseline results. This ensures alignment with the original findings before extending the analysis in later tasks. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.

>>>>

Building on these foundations, Assignment III investigates the informativeness of quarterly earnings announcements and their contribution to annual share price movements. The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets. By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting. At the same time, earnings reports may play a crucial role in contracting by influencing managerial compensation, debt agreements, and other contractual mechanisms tied to financial performance [@ball_how_2008]. The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively. Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S. country to explore cross-market variations.

@@

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task1 follows an exact replication approach by replicating key tables and figures from the original study using US data (1972–2006) to establish baseline results. @sec-task2 extends the analysis through empirical generalization, applying the same methodology to 2007–2023 US data to compare how results evolve over time. @sec-task3 employs a generalization and extension approach by applying the methodology to a non-US country, requiring adjustments for different databases and market structures. This framework aligns with the replication taxonomy outlined by @salterio_replication_2022. Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper, following Bloomfield’s (2016) triangulation principle. The concluding remarks are provided in @sec-conclusion.

@@

Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results. This ensures alignment with the original findings before extending the analysis in later tasks. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.
